### 2021-08-23 README.Rmd
edit the documentation of data pre-processing and example in readme.

wages_hs2020 <- as_tsibble(x = wages_hs2020,
                    key = id,
                    index = year,
                    regular = FALSE)

ggplot(wages_hs2020, 
       aes(x = year,
                y = mean_hourly_wage,
                group = id)) +
  geom_line(alpha = 0.7) +
  facet_sample() +
  ylab("mean hourly wage") +
  theme_bw()
```

>>>>

ggplot(wages_hs, 
       aes(x = year,
                y = mean_hourly_wage,
                group = id)) +
  geom_line(alpha = 0.7) +
  facet_sample() +
  ylab("mean hourly wage") +
  theme_bw()
```

## About the package name

A [yowie](https://en.wikipedia.org/wiki/Yowie) is a mythical creature in Australian foklore akin to Big Foot or Sasquatch in north America. In terms of the package it can be considered an acronym: Years Of Wages to Investigate and Explore.
